### 2020-01-30 wuhan.tex
suddenly work on other stuff

\section{newResults}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{compare_assumption.pdf}
\caption{
\textbf{Comparisons of estimated and assumed parameter values with their average values calculated from the multilevel model.}
I'm a caption; \emph{no, you're not.}
}
\label{fig:assumption}
\end{figure}

\fref{assumption} compares the estimated (or assumed) values of the exponential growth rate $r$, mean generation interval $\bar G$, and the squared CV $\kappa$ of the generation-interval distribution with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) that we calculate from our multilevel model.
We find that there is a large uncertainty associated with the underlying parameters;
many models rely on stronger assumptions that ignore these uncertainties.
Surprisingly, no studies take into account how the variability in generation intervals (represented by $\kappa$) affects their estimates of $\mathcal R_0$, even though the assumed values range from 0 to 0.5 across different studies.

@@

\fref{eff} demonstrates the degree to which how the uncertainty in each parameter propogates to the uncertainties in $\mathcal R_0$.
\swp{JD: can you explain figure 2?}

Finally, we assess the validity of estimates of $\mathcal R_0$ across different studies by 
replacing the their values of $r$, $\bar G$, and $\kappa$ with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) one at a time and recalculating the basic reproductive number $\mathcal R_0$ (\fref{R0}).
We find that incorporating uncertainties one at a time increases the width of the confidence intervals in most cases (16 out 18).
We estimate narrower confidence intervals for Study 2 when we use our pooled estimate of the squared CV in generation time $\mu_\kappa$ to recalculate $\mathcal R_0$ because they assume a narrow generation-interval distribution ($\kappa=0$);
when lower values of $\kappa$ are used, their estimates of $\mathcal R_0$ become less sensitive to the values of $r$ and $\bar G$.
We estimate narrower confidence intervals for Study 5 when we use our pooled estimate of the mean generation time $\mu_G$ to recalculate $\mathcal R_0$ because the range of uncertainty in the mean generation time $\bar G$ they consider is much wider than ours (\fref{assumption}).

>>>>

\section{Results}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{compare_assumption.pdf}
\caption{
\textbf{Parameter values.}
We inferred point estimates, uniform distributions (shown in orange) or confidence intervals (purple) for each parameter from each study, and combined them into pooled estimates (see text).
}
\label{fig:assumption}
\end{figure}

\fref{assumption} compares the estimated (or assumed) values of the exponential growth rate $r$, mean generation interval $\bar G$, and the squared CV $\kappa$ of the generation-interval distribution with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) that we calculate from our multilevel model.
We find that there is a large uncertainty associated with the underlying parameters;
many models rely on stronger assumptions that ignore these uncertainties.
Surprisingly, no studies take into account how the variability in generation intervals (represented by $\kappa$) affects their estimates of $\mathcal R_0$, even though the assumed values range from 0 to 0.5 across different studies.
It is also interesting that none of the six studies explicitly or implicitly assumed an exponentially distributed generation interval.

@@

\fref{eff} shows the effects of propagating uncertainty in different combinations would affect estimates and CIs for our pooled estimates, which represent a reasonable proxy for the state of knowledge as of 26 January. 
Propagating error from the growth rate (which all but one of the models did) is absolutely crucial. 
Propagating error from the generation interval also has important effects, however.
Once these two are included, the impact of leaving out uncertainty in the dispersion would be small, in this particular example.

We also evaluate the estimates of $\mathcal R_0$ across different studies by 
replacing the their values of $r$, $\bar G$, and $\kappa$ with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) one at a time and recalculating the basic reproductive number $\mathcal R_0$ (\fref{R0}).
We find that incorporating uncertainties one at a time increases the width of the confidence intervals all but two cases.
We estimate narrower confidence intervals for Study 2 when we use our pooled estimate of the squared CV in generation time $\mu_\kappa$ to recalculate $\mathcal R_0$ because they assume a narrow generation-interval distribution ($\kappa=0$);
when lower values of $\kappa$ are used, their estimates of $\mathcal R_0$ become less sensitive to the values of $r$ and $\bar G$.
We estimate narrower confidence intervals for Study 5 when we use our pooled estimate of the mean generation time $\mu_G$ to recalculate $\mathcal R_0$ because the range of uncertainty in the mean generation time $\bar G$ they consider is much wider than ours (\fref{assumption}).
